---
title: "carePlan_getItemValues"
output: html_document
author: Joseph Park
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load configuration settings. Password requested by rstudioapi.

```{r}
dbdriver <- 'PostgreSQL'
host  <- 'localhost'
port  <- '5432'
user  <- 'josephpark'
dbname <- 'eicu'
schema <- 'eicu'
options <- paste("--search_path=", schema, sep="")
```

Connect to database.

```{r}
require("RPostgreSQL")
drv <- dbDriver(dbdriver)
con <- dbConnect(drv, dbname = dbname,
                 host = host, port = port,
                 user = user, password = rstudioapi::askForPassword("Database password"),
                 options = options)
dbExistsTable(con, "patient")
```

Write cplitemvalues to file "possible_status" for inspection on which items indicate patient code status.
All cplitemvalues that were chosen were in cplgroup = 'Care Limitation' (all cplitemvalues in this cplgroup was used),
  except cplitemvalue = 'End of life', which was in cplgroup = 'Ordered Protocols'.
SQL command was generated using show_query() for possible_status

```{r, connection = con}
library(dplyr)
carePlanGeneral_tbl <- tbl(con, "careplangeneral")
possible_status <- carePlanGeneral_tbl %>% 
  group_by(cplitemvalue) %>%
  summarize(n=n()) %>%
  arrange(desc(n))
write.csv(possible_status, "possible_status.csv")
```
