---
title: "carePlan_getPatientCode"
output: html_document
author: Joseph Park
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load configuration settings. Password requested by rstudioapi.

```{r}
dbdriver <- 'PostgreSQL'
host  <- 'localhost'
port  <- '5432'
user  <- 'josephpark'
dbname <- 'eicu'
schema <- 'eicu'
options <- paste("--search_path=", schema, sep="")
```

Connect to database.

```{r}
require("RPostgreSQL")
drv <- dbDriver(dbdriver)
con <- dbConnect(drv, dbname = dbname,
                 host = host, port = port,
                 user = user, password = rstudioapi::askForPassword("Database password"),
                 options = options)
dbExistsTable(con, "patient")
```

After inspecting table generated from careplan_getitemvalues.Rmd, the values in cpitemvalue_code were selected to relate to patient code status.

```{r, connection = con}
library(dplyr)
carePlanGeneral_tbl <- tbl(con, "careplangeneral")
cplitemvalue_code = c('Full therapy', 'Do not resuscitate', 'No CPR', 'No intubation', 'Comfort measures only',
                      'No cardioversion', 'No vasopressors/inotropes', 'No augmentation of care', 
                      'End of life', 'No blood products', 'No blood draws', 'Advance directives')
```

Generate table that lists the patient along with code status.
SQL command was generated using show_query() for patientCodeStatus

```{r, connection = con}
patientCodeStatus <- carePlanGeneral_tbl %>%
  filter(cplitemvalue %in% cplitemvalue_code) %>%
  select(patientunitstayid, cplitemoffset, cplgroup, cplitemvalue) %>%
  arrange(patientunitstayid, cplitemoffset, cplitemvalue) %>%
  group_by(patientunitstayid, cplitemoffset) %>%
  summarize(cplitemvalue = paste(cplitemvalue, collapse=", "))
patientCodeStatus
```

Output the file as a csv.

```{r, connection = con}
write.csv(patientCodeStatus, "patient_status_table.csv", row.names=FALSE)
```

Optional: sorts patients by which patient had the most number of status updates. 

```{r, connection = con,eval=FALSE}
patientCodeStatus %>%
  group_by(patientunitstayid) %>%
  summarize(n = n()) %>%
  arrange(desc(n))
```

Example of a patient. This patient was strange with both full therapy and no CPR at the same time.

```{r, connection = con,eval=FALSE}
patientCodeStatus %>%
  filter(patientunitstayid == 266999)
```
